Spatial Reasoning and Statistical Graphics

### 2014-10-22 Paper/Draft1/TestingVisualAptitude.Rnw
Nicer table for pca summary

<<correlations, echo=F, comment="|", warning=F, message=F, results='asis'>>=
print(xtable(cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")]), digits=c(1, rep(3, 5)), caption="Correlation matrix for the five tests."), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize)
@
<<pcatests,echo=F, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".45\\linewidth", fig.height=4.5, fig.width=4.5, warning=F, message=F>>=
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
summary(pca)
screeplot(pca)
@
<<pcarotation,echo=F, results='asis'>>=
print(xtable(pca$rotation, caption="PCA Rotation matrix for all five tests."), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize)
@

>>>>

<<correlations, echo=F, comment="|", warning=F, message=F, results='asis'>>=
print(xtable(cor(ans.summary[,c("lineup","card_rot", "fig_class", "folding", "vis_search")]), digits=c(1, rep(3, 5)), caption="Correlation matrix for the five tests."), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize)
@
<<pcatests,echo=F, fig.cap="Scree plot of principle component analysis of performance on the different test batteries.", out.width=".45\\linewidth", fig.height=4.5, fig.width=4.5, warning=F, message=F>>=
pca <- prcomp(ans.summary[,c("lineup", "card_rot", "fig_class", "folding", "vis_search")], scale=T, retx=T)
screeplot(pca)
@
<<pcarotation,echo=F, results='asis'>>=
print(xtable(summary(pca), caption="Importance of components in principal component analysis of the five tests."), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize)
print(xtable(pca$rotation, caption="PCA Rotation matrix for all five tests."), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize)
@
